Make figures for simple simulation with good and poor precision observations

### 2016-12-08 analysis/make_GOODPOOR_figs.Rmd
Made a few small adjustments to make_GOODPOOR_figs.Rmd.

```{r chunk-options, include=FALSE}
source("chunk-options.R")
```

First perform a simple simulated example to illustrate high and low signal.
True values of beta simulated from $(0.5 N(0,2^2) + 0.5 \delta_0)$.
```{r}
ntest = 10000
set.seed(112)
require(ashr)
require(qvalue)
require(locfdr)
require(mixfdr)
source("../R/plot_FDReg_hist.R")

null_alt = rbinom(ntest,1,0.5)
beta = rnorm(ntest,0,sd=1)
beta = ifelse(null_alt==1,beta,0)
GOOD= 1:(ntest/2)
sebetahat = rep(1,ntest)
sebetahat[-GOOD] = 10

@@

Show how poor precision observations dilute good ones:
```{r, GOODPOOReg_hist, dev='pdf',fig.width=6.5, fig.height=3}
par(mai=c(0.3,0.3,0.2,0.2),mgp = c(3, 0.5, 0))
layout(matrix(1:3,ncol=3,byrow=TRUE))
plot_FDReg_hist(pval[GOOD],1,type=1,title="Good-precision observations",ylab="",nc=20,cex.axis=1,cex.main=1.2,ylim=c(0,2.5))
plot_FDReg_hist(pval[-GOOD],1,type=1,title="Poor-precision observations",ylab="",nc=20,yaxt='n',cex.axis=1,cex.main=1.2,ylim=c(0,2.5))
axis(side=2, labels=FALSE,tck=-0.01)
plot_FDReg_hist(pval,1,type=1,title="Combined",yaxt='n',ylab="",nc=20,cex.axis=1,cex.main=1.2,ylim=c(0,2.5))
axis(side=2, labels=FALSE,tck=-0.01)
```

>>>>

First, we load the necessary libraries, and specify settings for displaying 
the plots in the rendered document.

```{r chunk-options, include=FALSE}
library(ashr)
library(qvalue)
library(locfdr)
library(mixfdr)
source("chunk-options.R")
source("../R/plot_FDReg_hist.R")
```

Create a simple simulated data set to illustrate high and low signal. True 
values of beta simulated from $(0.5 N(0,2^2) + 0.5 \delta_0)$.

```{r sim_data}
ntest = 10000
set.seed(112)

null_alt  = rbinom(ntest,1,0.5)
beta      = rnorm(ntest,0,sd=1)
beta      = ifelse(null_alt==1,beta,0)
GOOD      = 1:(ntest/2)
sebetahat = rep(1,ntest)
sebetahat[-GOOD] = 10

@@

Show how poor precision observations dilute good ones.

```{r GOODPOOReg_hist, dev='pdf', fig.width=6.5, fig.height=3}
par(mai = c(0.3,0.3,0.2,0.2),mgp = c(3, 0.5, 0))
layout(matrix(1:3,ncol = 3,byrow = TRUE))
plot_FDReg_hist(pval[GOOD],1,type = 1,title = "Good-precision observations", 
                ylab = "",nc = 20,cex.axis = 1,cex.main = 1.2,ylim = c(0,2.5))
plot_FDReg_hist(pval[-GOOD],1,type = 1,
                title = "Poor-precision observations",ylab = "",nc = 20,
                yaxt = 'n',cex.axis = 1,cex.main = 1.2,ylim = c(0,2.5))
axis(side = 2, labels = FALSE,tck = -0.01)
plot_FDReg_hist(pval,1,type = 1,title = "Combined",yaxt = 'n',ylab = "",
                nc = 20,cex.axis = 1,cex.main = 1.2,ylim = c(0,2.5))
axis(side = 2, labels = FALSE,tck = -0.01)
```
